### 2021-07-10 submission.tex
Dijkstra

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{graphicx}

\usepackage[top=2.5cm, left=3cm, right=3cm, bottom=4.0cm]{geometry}

@@

\section*{Question 5} 
\begin{enumerate}[label = (\alph*)]
    \item
    \begin{enumerate}[label = (\roman*)]
    \item

	\end{enumerate}
\end{enumerate}

>>>>

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{fancyvrb}
\usepackage{alltt}
\usepackage[top=2.5cm, left=3cm, right=3cm, bottom=4.0cm]{geometry}

@@

\section*{Question 5} 
\begin{enumerate}[label = (\alph*)]
    \item
    \begin{enumerate}[label = (\roman*)]
    \item
    G = <V, E, W>

    E - associations between two consecutive words

    W - ???

    \begin{Verbatim}[tabsize=4]
    	def Dijkstra(G, W, src):
    		# preparation
    		Q = prior_queue()
    		dist = map(cardiality(G))
    		back_ptrs = map(cardiality(G))
    		for v in G:
    			if v == src: 
    				disv[v] = 0
    			else:
    				dist[v] = inf
    			back_ptrs[v] = null
    			Q.add(src, dist(src))

    		#main part
    		while !Q.is_empty():
    			u = Q.get_min()
    			for v in neighbours(u):
    				d = dist[u] + W[V]
    				if d < dist[v]:
    					dist[v] = d
    					back_ptrs[v] = u
    					Q.decrease_prior(v, d)
    		return dist, back_ptrs
    	\end{Verbatim}

    	\item
    	Dijkstra: $O((|V|+|E|) \cdot log(|V|))$

    	Viterbi: $O(T^2 \cdot |S|) = O(|E|)$

    	Dijkstra algorithm is faster under the following condition:

    	 $(|V|+|E|) \cdot log(|V|) < |E|$

	\item

	\begin{enumerate}[label = (\roman*)]
    \item
       \begin{alltt}
    	def Dijkstra(G, W, src):
    	    # preparation
    	    ...
    	    #main part
    	    while !Q.is_empty():
    	        u = Q.get_min()
    	        for v in neighbours(u):
    	            d = \(\bigoplus \)(dist[u] \(\bigotimes \) W[v])
    	            dist[v] = d
    	            back_ptrs[v] = arg(d)
                Q.decrease_prior(v, d)
    		return dist, back_ptrs
    	\end{alltt}
